Visual Question Answering with DeepProbLog

### 2022-03-25 paper/paper.tex
Add code repository to paper

\author{Jorrit Willaert$^{1}$ \\
	\normalsize $^{1}$Catholic University of Leuven, Leuven -- Belgium \\
	\normalsize e-mail: jorrit.willaert@student.kuleuven.be
}

@@

\section{EXPERIMENTS}
\label{sec:experiments}
The main focus of this paper is to outline the advantages of using a Neuro Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach. Therefore, a neural network based approach had to be implemented. Not all details will be listed here, but the main idea is that the image has to be fused with the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6. Hence, the neural network will have 10 output nodes. Care has been taken for class skew, by introducing weights in the loss function.}. The general structure of this network is given in Figure \ref{fig:pure_nn_network}.

@@

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_2x2.png} 
    \captionsetup{justification=centering}
    \caption{DeepProbLog 2x2: Loss curve}
    \label{fig:loss_curve_deepproblog_2x2}
    \end{center}
\end{figure}

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_2x2.png} 
    \captionsetup{justification=centering}
    \caption{Pure NN based approach 2x2: Loss curve}
    \label{fig:loss_curve_pure_NN_2x2}
    \end{center}
\end{figure}
An extremely important remark to be made is the difference between `number of iterations' and `number of epochs'. By the number of iterations, the number of forward and backward passes of a batch (with size 32) is meant, whereas the number of epochs denotes the number of times all the images of the training set are forward and backwardly passed. In this application, a training size of 10 000 was used, hence one epoch consists of 312.5 iterations.

@@

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{loss_curve_deepproblog_6x6.png} 
    \captionsetup{justification=centering}
    \caption{DeepProbLog 6x6: Loss curve}
    \label{fig:loss_curve_deepproblog_6x6}
    \end{center}
\end{figure}

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.45\textwidth]{loss_curve_pure_NN_6x6.png} 
    \captionsetup{justification=centering}
    \caption{Pure NN based approach 6x6: Loss curve}
    \label{fig:loss_curve_pure_NN_6x6}
    \end{center}
\end{figure}

>>>>

\author{Jorrit Willaert$^{1}$ \\
	\normalsize $^{1}$Catholic University of Leuven, Leuven -- Belgium \\
	\normalsize e-mail: jorrit.willaert@student.kuleuven.be \\
    \normalsize code repository: https://github.com/JorritWillaert/Capita-Selecta-Neuro-Symbolic-AI
}

@@

\section{EXPERIMENTS}
\label{sec:experiments}
The main focus of this paper is to outline the advantages of using a Neuro Symbolic AI approach (offered by the DeepProbLog framework), instead of a purely neural network based approach. Therefore, a neural network based approach had to be implemented. Not all details will be listed here, but the main idea is that the image has to be fused whttps://github.com/JorritWillaert/Capita-Selecta-Neuro-Symbolic-AIith the question, after which a prediction can be made\footnote{Possible answers on the questions are: rectangle, circle, yes, no, 1, 2, 3, 4, 5 and 6. Hence, the neural network will have 10 output nodes. Care has been taken for class skew, by introducing weights in the loss function.}. The general structure of this network is given in Figure \ref{fig:pure_nn_network}.

@@

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{loss_curve_deepproblog_2x2.png} 
    \captionsetup{justification=centering}
    \caption{DeepProbLog 2x2: Loss curve}
    \label{fig:loss_curve_deepproblog_2x2}
    \end{center}
\end{figure}

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{loss_curve_pure_NN_2x2.png} 
    \captionsetup{justification=centering}
    \caption{Pure NN based approach 2x2: Loss curve}
    \label{fig:loss_curve_pure_NN_2x2}
    \end{center}
\end{figure}
An extremely important remark to be made is the difference between `number of iterations' and `number of epochs'. By the number of iterations, the number of forward and backward passes of a batch (with size 32) is meant, whereas the number of epochs denotes the number of times all the images of the training set are forward and backwardly passed. In this application, a training size of 10 000 was used, hence one epoch consists of 312.5 iterations.

@@

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{loss_curve_deepproblog_6x6.png} 
    \captionsetup{justification=centering}
    \caption{DeepProbLog 6x6: Loss curve}
    \label{fig:loss_curve_deepproblog_6x6}
    \end{center}
\end{figure}

\begin{figure}[htp]
    \begin{center}
    \includegraphics[width=0.40\textwidth]{loss_curve_pure_NN_6x6.png} 
    \captionsetup{justification=centering}
    \caption{Pure NN based approach 6x6: Loss curve}
    \label{fig:loss_curve_pure_NN_6x6}
    \end{center}
\end{figure}
